### 2021-09-03 RR-9418.tex
minor typo fixes

\RRNo{9418}
\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  %%  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  %% \thanksref{aff1}
  \and
  Alexandre Van Kempen
  %% \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

\RRabstract{
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  contents closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall. Unfortunately, locating the closest replica of a specific
  content requires indexing \emph{every live} replica along with its
  \emph{location}.
  %
  Relying on remote services contradicts with the properties of Edge
  infrastructures as locating replicas may effectively take more time
  than actually downloading contents.  At the opposite, maintaining
  such an index at every \process would prove overly costly in terms
  of memory and traffic, especially since \processes can create and
  destroy replicas at any time.

@@

\makeRR
\RRNo{9418}

>>>>

\RRdate{September 2021}
% \RRVersion{2}
% \RRdater{<Another date for version 2>}
\RRauthor{
  Adrien L{\`e}bre
  %%  \thanks[aff1]{Inria}
  \and
  Brice N{\'e}delec
  %% \thanksref{aff1}
  \and
  Alexandre Van Kempen
  %% \thanksref{aff1}
}
\authorhead{L{\`e}bre, N{\'e}delec, Van Kempen}
\RRtitle{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français long
\titlehead{\NAME : Confiner le trafic de l'indexation décentralisée de contenu au niveau du Edge} %% titre français court
\RRetitle{\NAME: Lock Down the Traffic of Decentralized Content Indexing at the Edge}

@@

\RRabstract{
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  content closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall. Unfortunately, locating the closest replica of a specific
  content requires indexing \emph{every live} replica along with its
  \emph{location}.
  %
  Relying on remote services enters in contradiction with the
  properties of Edge infrastructures as locating replicas may
  effectively take more time than actually downloading content.  At
  the opposite, maintaining such an index at every \process would
  prove overly costly in terms of memory and traffic, especially since
  \processes can create and destroy replicas at any time.

@@

\RRNo{9418}
\makeRR
